%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {NeuroAI Trainee} % Job title
    {\href{https://neuromatch.io/}{Neuromatch Academy}} % Organization
    {Remote} % Location
    {Summer 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in an interdisciplinary {\textbf{NeuroAI course}}, studying principles of natural and artificial intelligence, and gaining practical experience in {\textbf{implementing and analyzing NeuroAI models}}.}
        \item {Conducted research on {\textbf{macro learning}}, focusing on {\textbf{biologically inspired ANN architectures}} derived from C.elegans motor circuits for controlling simulated agents.}
        \item {Developed and compared bio-inspired ANNs with traditional MLPs, analyzing performance, sample efficiency, and robustness across various environmental conditions and control tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computational Neuroscience Trainee} % Job title
    {\href{https://neuromatch.io/}{Neuromatch Academy}} % Organization
    {Remote} % Location
    {Summer 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Acquired proficiency in {\textbf{computational neuroscience}} through active participation in tutorials during a 3-week academic journey.}
        \item {Contributed to a group project centered around {\textbf{"Optimal Control and Motor Learning"}}, applying {\textbf{statistical data analysis}} techniques and {\textbf{machine learning}} methods.}
        \item {Collaborated with team members to explore the potential application of optimal control theory in characterizing {\textbf{motor learning}} patterns within the joystick dataset from ECoG datasets by Miller (2019).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {\href{https://www.ipm.ac.ir/}{Institute for Research in Fundamental Siences (IPM)}} % Organization
    {Tehran, Iran} % Location
    {Summer 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Accelerated bsbf min-sum decoder algorithm using {\textbf{bit-slicing}} on Nvidia GPUs by {\textbf{CUDA}}. Submitted research to IEEE Transactions on Parallel and Distributed Systems (TPDS) for peer review.}
        \item {Working on implementation of CORDIC algorithm using bit-slice approach.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Intern} % Job title
    {\href{https://rahnemacollege.com/}{Rahnema College}} % Organization
    {Tehran, Iran} % Location
    {Summer 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a web crawler detection model using {\textbf{unsupervised}} learning approaches.}
	\item{Workshops included {\textbf{mathematics}}, {\textbf{machine learning}}, {\textbf{deep learning}}, {\textbf{big data}} and {\textbf{soft skills}}.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Development Intern} % Job title
    {Classgram} % Organization
    {Tehran, Iran} % Location
    {Summer 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {A backend development internship focused on the {\textbf{Django REST}} framework.}
        \item {Fixed some minor bugs on some of the endpoints and implemented i18n feature}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
